---
output:
  officedown::rdocx_document:
    reference_docx: "custom-reference.docx"
params:
  SAN: "NA"
  Sample_ID: "NA"
  Host: "NA"
  H_type: "NA"
  Cleavage_site: "NA"
  phylo_tree_Src: "NA"
  aa_seq_src: "NA"
  output: "NA"
---


```{r setup, include=FALSE, warning = FALSE}
library(knitr)
library(dplyr)
library(officedown)
library(officer)
library(rmarkdown)
library(ggmsa)
library(ggplot2)
library(yaml)
library(flextable)

# set chunks defaults
knitr::opts_chunk$set(
  echo       = FALSE,
  message    = FALSE,
  warning    = FALSE
)


# now read data for making the report

SAN <- params$SAN
Sample_ID <- params$Sample_ID
Host <- params$Host
H_type <- params$H_type
Cleavage_site <- params$Cleavage_site
phylo_tree_Src <- params$phylo_tree_Src
aa_seq_src <- params$aa_seq_src


#Figure and table formatting

Figure_numbers <- run_autonum(seq_id = "Figure", pre_label = "Fig. ", bkm = NULL)
Table_numbers <- run_autonum(seq_id = "Table", pre_label = "Table ")


```

# Next Generation Sequencing Analysis for SAN `r SAN`

This analysis provides an identity analysis of the whole genome sequence data generated at ACDP (AAHL) `r SAN` samples.

**Interpretation**

The HA gene sequence data suggests that the detected virus is most similar to ...

* Dot point 1
* Dot point 2

**This analysis contains:**

1. Sample information from which sequences were obtained
2. Phylogenetic tree showing the relationship of sample `r SAN` with other viruses
3. HA sequence alignment comparison to virus sequence with ...
4. BLAST results for each gene segment for sample `r SAN`

```{r}
block_section(prop_section(type = "continuous"))
```

## 1. Sample information from which sequences were obtained**

Avian influenza A virus (AIV) whole genome sequences of the XXXX subtype was generated directly from the samples as shown in Table 1.
All XXXX samples shared XXXX% nucleotide and XXXX% amino acid similarity for the eight viral segments.

```{r summary-table}

#Table caption

fpar(Table_numbers,
  ftext(
  paste(SAN, "AIV PCR positive samples from which virus sequences were obtained", sep = " "), 
  fp_text(italic = TRUE)),
  fp_p = fp_par(padding.bottom = 10)
  )

#Table data 

Table_1_dataset <- matrix(c(SAN, Sample_ID, Host, H_type, Cleavage_site), ncol = 5)
colnames(Table_1_dataset) <- c("ACDP (AAHL) Sample No.", "Sample ID", "Host", "Subtype", "HA cleavage site sequence")
Table_1_dataset <- as.data.frame(Table_1_dataset)

#Table formatting

thick_border = fp_border(color="black", width = 2)
thin_border = fp_border(color="gray", width = 0.5)

flextable(Table_1_dataset)%>%
  fontsize(part = "all", size = 10) %>%
  bold(i = 1, part = "header") %>%
  align(align = "center", part = "all") %>%
  set_table_properties(width = 1, layout = "autofit") %>%
  padding(padding = 5, part = "all") %>%
  border_remove() %>%
  border_outer(part="all", border = thick_border)%>%
  border_inner_v(part = "all", border = thin_border)
  
block_section(
  prop_section(
      page_size = page_size(orient = "portrait"),
      type = "continuous"
  )
)

```

```{r amino-acid-sequence, fig.asp = 0.3, fig.width = 10}

#Figure function

p <- ggmsa(aa_seq_src,
      char_width = 0.9,
      seq_name = TRUE,
      color = "Chemistry_AA" ) +
  facet_msa(field = 70) 

dummy <- subset(p$layers[[1]]$data,  facet == 0)

p + geom_rect(data = dummy, mapping = aes(xmin = 40.5, xmax = 50, ymin = -Inf, ymax = Inf),
 color = "black", size = 1.5, fill = NA) 

#Figure caption

fpar(Figure_numbers,
  ftext(
  paste(SAN, H_type, "HA amino acid sequence alignment. Position of the multi-basic HA cleavage site is indicated by the black box.", sep = " "), fp_text(italic = TRUE)),
fp_p = fp_par(text.align = "center"))

block_section(
  prop_section(
      page_size = page_size(orient = "landscape"),
      type = "continuous"
  )
)

```


```{r phylogenetic-tree-image}

#Figure placement

fpar(
external_img(src = phylo_tree_Src, height = 7.87, width = 6.5),

fp_p = fp_par(text.align = "center")
)

#Figure caption

fpar(Figure_numbers,
  ftext(
  paste("Phylogenetic tree based on near full-length", H_type,"HA gene sequences (1648bp) showing the relationship of sample", SAN, "(Red) to other endemic and exotic", H_type, "HA viruses.", sep = " "), fp_text(italic = TRUE)),
fp_p = fp_par(text.align = "left", border = fp_border(color = "black", style = "solid", width = 0.5)))



```
